Behavior Driven Development in Haskell

### 2012-05-23 paper.tex
adding memo and advice from "How to write a great research paper".

\begin{abstract}
TBD: This is the text of the abstract.
\end{abstract}

@@

@@

\begin{itemize}
\item Introduced doctest from Python community to Haskell community
\item Introduced *spec from Ruby community to Haskell community
\item Integrated doctest and QuickCheck
\item Show best current practice of design/documentation/tests
\end{itemize}

@@

Should talk about equation property.

@@

@@

>>>>

\begin{abstract}

State the problem.

Say why it’s an interesting problem.

Say what your solution achieves.

Say what follows from your solution.

\end{abstract}

@@

%%%% Describe the problem.

TBD: Strong type system.

TBD: Tend not to write tests

The purpose of this paper is to
encourage Haskllers to write documentation, which can be used for testing, in their libraries.

%%%% State your contributions.

@@

\begin{itemize}
\item Introduced {\tt doctest} from Python community to Haskell community
and integrated it with QuickCheck (Section XXX)
\item Introduced {\tt hspec} from Ruby community to Haskell community and
integrated it with QuickCheck (Section XXX)
\item Show best current practice of design/documentation/tests (Section XXX)
\end{itemize}

@@

Haddock example and doctest.

Should talk about equation property. (e.g. container)
Quickcheck.

pure vs IO.

@@

FIRST convey the idea.

\subsection{Tests suitable with doctest}

\subsection{Tests suitable with hspec}

\subsection{Integrating multiple test suites}

\section{Best current practice}

undefined.

@@

\section{Related work}

literate programming.

hunit.

test-framework.

smallCheck.

And others?
